%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{bibentry}
\usepackage{apacite}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Large \scshape Abhinandan Pathak} \\ \vspace{1pt}
    \small 8209031619 $|$ \href{mailto:x@x.com}{\underline{abhinandanpathak87@gmail.com}} $|$ 
    \href{https://linkedin.com/in/abhinandan-pathak-0abbaa176/}{\underline{LinkedIn}} $|$
    \href{https://github.com/abhinandan1999/Learning}{\underline{Github}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Science Associate Consultant}{July 2023 -- Present}
      {ZS Associates}{Bangalore, KA}
      \resumeItemListStart
        \resumeItem{Collaborating with multiple teams to understand the impact of recommendations sent.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Data Science Associate}{June 2021 - June 2023}
      {ZS Associates}{Bangalore, KA}
      \resumeItemListStart
        \resumeItem{Communicated with clients to understand the requirements    and framed it into problem statements}
        \resumeItem{Worked as a developer on a ML based recommendation engine product for a fortune 500 pharmaceutical clients}
        \resumeItem{Mentored colleagues to quickly get on-boarded on existing projects.}
        
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Analytics commercial engine} $|$ \emph{Python, PySpark, Docker, Git, Bitbucket, Airflow, Kedro, S3}}{}
          \resumeItemListStart
            \resumeItem{Scaled this product to various drugs}
            \resumeItem{Integrated a sequence recommendation through various promotional channels.}
            \resumeItem{Retrained the ML models as and when data drifted or model performance decreased.}
            \resumeItem{Created features for modelling from raw data.}
            \resumeItem{Automated the process of delivering files to Business users for review.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{JET} $|$ \emph{Python, PySpark, Git, Bitbucket, DataIKU}}{}
          \resumeItemListStart
            \resumeItem{Hard retrain the ML models for various brands and deploy them to production.}
            \resumeItem{Complete ownership of deliverable of results on time to marketing team.}
            \resumeItem{Created complete timeline for ML Operations to get maximum impact.}
            \resumeItem{Delivered and communicated the results to clients.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Promotion Response and Touchpoint Optimization} $|$ \emph{Python, Gekko, Statsmodel, Databricks, S3}}{}
          \resumeItemListStart
            \resumeItem{Processed the marketing and Sales data for it to be ready for modelling.}
            \resumeItem{Created a Linear regression model to understand the impact of promotion on Sales.}
            \resumeItem{Optimized the allocation of budget to different promotional channels to generate maximum revenues.}
            \resumeItem{Deployed the final pipeline on Databricks}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical and Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Pyspark, SQL, C/C++, Matlab, R} \\
     \textbf{Deep learning Frameworks}{: Pytorch, Tensorflow} \\
     \textbf{ML Libraries}{: ScikitLearn, Statsmodels, Optuna, HyperOpt, Numpy, Pandas} \\
     \textbf{ML models}{: Linear Regression, Logistic Regression, Random Forest, XGBoost, LGBM, Transformers} \\
     \textbf{Developer Tools}{: Git, Docker, Visual Studio Code, JIRA} \\
     \textbf{Orchestration Tools}{: DataIKU, Airflow} \\
     \textbf{Presentation Tools}{: MS Powerpoint, MS Excel, MS Word} \\
     \textbf{Soft Skills}{: Client Communications (US and APAC region)}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology Karnataka}{9.01 CGPA}
      {Bachelor of Technology in Electrical and ELectronics Engineering}{Aug. 2017 -- May 2021}
    \resumeSubheading
      {The Oxford senior secondary School}{93.4 \%}
      {AISSCE-CBSE}{April. 2014 -- Mar 2016}
  \resumeSubHeadingListEnd

 
%-----------Publications-----------
\nobibliography{publications.bib}
\bibliographystyle{unsrt}
\section*{Publications}
  \begin{enumerate}
    \item \bibentry{9597799}
    (\href{https://ieeexplore.ieee.org/document/9597799}{\underline{PublicationLink}})

  \item \bibentry{patent}
  (\href{https://www.nitk.ac.in/patent-granted-to-dr-tukaram-moger-team}{\underline{PatentLink}})
  \end{enumerate}

%-------------------------------------------
\end{document}
